%----------------------------------------------------------------------------------
% LaTeX SETUP
%----------------------------------------------------------------------------------
% Document class
\documentclass[11pt,letterpaper,sans]{moderncv}

% Modern CV themes
\moderncvstyle{banking}                         % 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}                            % 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

\usepackage[utf8]{inputenc}                     % UTF8 encoding
\usepackage{eurosym}                            % Use the Euro sign 
\usepackage{graphicx}                           % Hide keywords for searchable text
\usepackage{xcolor}                             % Use xcolor
\usepackage{import}                             % Use import
\usepackage[scale=0.91]{geometry}               % adjust the page margins

\nopagenumbers{}                                % No page numbers
\def\hide#1{\scalebox{.01}{\color{white}#1}}    % Hidden text for keyword scraping
%\setlength{\hintscolumnwidth}{3cm}             % Change the width of the date column
%\setlength{\makecvtitlenamewidth}{10 cm}       % Title name width adjustments 
%\renewcommand{\familydefault}{\sfdefault}      % Use to set the default font

% Adjust the spacing between title and address
\makeatletter
\patchcmd{\makehead}{%search
    \ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}\\%
    }{%replace
    \ifthenelse{\equal{\@title}{}}{}{\titlestyle{~|~\@title}}\\[0.10cm]%
  }{%success
  }{%failure
  }
\makeatother

% Adjust the spacing between address and contact info
\makeatletter
\patchcmd{\makehead}{%search
  \flushmakeheaddetails\@firstmakeheaddetailselementtrue\\\null}{%replace
  \flushmakeheaddetails\@firstmakeheaddetailselementtrue\par\vspace{-0.3cm}\null%
  }{%success
  }{%failure
  }
\makeatother

% Adjust the font size for the title
\renewcommand*{\namefont}{\fontsize{25}{40}\mdseries\upshape}
\renewcommand*{\titlefont}{\fontsize{25}{40}\mdseries\upshape}

%----------------------------------------------------------------------------------
% HEADER
%----------------------------------------------------------------------------------
\name{Davide Lorenzo}{Asnaghi}          % Name    
\title{M.Eng.}                          % Educational title
\address{New York}{NY, 10280}{USA}      % Address
\phone{+1 510 (944) 9620}               % [optional] mobile phone
%\phone[fixed]{01234 123456}            % [optional] fixed phone
%\phone[fax]{+3~(456)~789~012}          % [optional] fax phone
\email{asnaghi@me.com}                  % [optional] email
\homepage{asnaghi.me}                   % [optional] website
%\extrainfo{additional information}     % [optional] additional info
%\photo[64pt][0.4pt]{picture}           % [optional] photo (height)(frame thickness)
%\quote{Some quote}                     % [optional] quote
\social[linkedin]{d-asnaghi}            % [optional] social profile (website)

%----------------------------------------------------------------------------------
% CONTENT
%----------------------------------------------------------------------------------
\begin{document}

\makecvtitle
\vspace*{-15mm}
\small{ }
        
     \section{Experience}
     
        \vspace{-1pt}
        \cventry{Aug 2019 -- Present}{Embedded engineer - C/C++ development for a portable ultrasound device}{Butterfly Network}{New York, USA}{}
        {
        \vspace{-1pt}
        \begin{itemize}
            \item Designed and implemented a robust, RAM to EEPROM based, field update process for the bootloader on a Cypress FX3.
            \item Wrote proprietary, size-constrained drivers in C and C++ for inertial measurement units (IMU) such as ICM20948 and MPU9250
        \end{itemize}
        } 
        
        \vspace{-1pt}
        \cventry{Mar 2019 -- Aug 2019}{Embedded engineering intern - R\&D for a new product line of Bluetooth smart stethoscopes}{Eko Devices}{Berkeley, USA}{}
        {
        \vspace{-1pt}
        \begin{itemize}
            \item Responsible for the firmware development of Eko's new smart stethoscope model, based on the Cypress PSoC6 BLE microcontroller.
            \item Implemented Bluetooth Low Energy (BLE) Over-The-Air (OTA) updates and physiological Digital Signal Processing (DSP) features.
        \end{itemize}
        } 
        
        \vspace{-1pt}
        \cventry{Aug 2018 -- Mar 2019}{Graduate student researcher - embedded electronics for physiological data acquisition}{Berkeley Emergent Space Tensegrities Lab.}{Berkeley, USA}{}
        {
        \vspace{-1pt}
        \begin{itemize}
            \item Lead designer of sensors for physiological data collection, focused on the integration of hardware, firmware, and validation studies.
            \item Created a customized MicroPython firmware on STM32 to allow easy modification of the core parameters by the rest of the team.
        \end{itemize}
        }
        
        \vspace{-1pt}
        \cventry{Sep 2017 -- Jun 2018}{Robotics Institute firmware engineering intern - CAN bus communication and sensor fusion}{DJI}{Hong Kong, HK}{}
        {
        \vspace{-1pt}
        \begin{itemize}
            \item Developed a modular C library for the control system of four motors robotic platforms, to be deployed in drones and ground robots.
            \item Designed a sensor-fusion based distance measurement system, using a Kalman filter with time of flight and infrared sensors.
        \end{itemize}
        } 
        
        \vspace{-1pt}
        \cventry{Jan 2016 -- Aug 2017}{Firmware engineer - electronics development}{Pluteus S.r.l.s}{Milan, IT}{}
        {
        \vspace{-1pt}
        \begin{itemize}
            \item Engineering lead for an early stage hardware startup focused on peer-to-peer object sharing based on NFC authentication.
            \item Designed the device's embedded architecture based on the STM32 platform controlling electromechanical devices and sensors.
        \end{itemize}
        } 
          \vspace{-13pt}
    
    \section{Education}
        
        \cventry{2018 -- 2019}{Master of Engineering, Biomedical engineering}{University of California, Berkeley}{Berkeley, USA}{\textit{GPA: 3.88}}{
        \vspace{-1pt}
        \begin{itemize}
            \item Graduate researcher at BEST Lab: embedded firmware development for physiological data acquisition and processing (ECG, EMG)
        \end{itemize}}
        \vspace{-1pt}
        
        \cventry{2017 -- 2018}{Bachelor of Engineering, Electronic Engineering}{The Hong Kong University of Science and Technology (HKUST)}{Hong Kong, HK}{\textit{GPA: 3.85}}{
        \vspace{-1pt}
        \begin{itemize}
            \item Undergraduate researcher at HKUST Robotics institute: embedded engineering for robotics systems, CAN bus communication
        \end{itemize}}
        \vspace{-1pt}
        
        \cventry{2015 -- 2017}{Bachelor of Science, Biomedical Engineering}{Politecnico di Milano}{Milan, IT}{\textit{GPA: 109/110 (3.96)}}{
        \vspace{-1pt}
        \begin{itemize}
            \item Undergraduate research associate at NECST Lab: FPGA design applied to biomedical science, hardware accelerated image processing
        \end{itemize}}
        \vspace{-1pt}
        
        \subsection{Publications}
        \vspace{-3pt}
        
            \cventry{2020}{Authors: Georgieu TA, Asnaghi D, Liang A, Agogino AM, ASME - Journal of Medical Devices}{\href{https://doi.org/10.1115/1.4043976}{The Sparthan Three-Dimensional Printed Exo-Glove: A Preliminary Evaluation of Performance}}{Berkeley, USA}{}{}
            \vspace{-1pt}
        
            \cventry{2019}{Authors: Wong TH, Asnaghi D, Leung W, International Conference on Engineering Design}{\href{https://doi.org/10.1017/dsi.2019.81}{Mechatronics enabling kit for 3D printed hand prostheses}}{Delft, NL}{}{}
            % \vspace{-5pt}
        
        % \subsection{Awards and Achievements}
        
        %     \textbf{Big Ideas, Hardware for Good:} \textit{Modular open source electronic development kit for medical devices, category winner \hspace*{\fill} May 2019}
        
            % \textbf{DJI Robomaster:} \textit{Mechatronics design for robotics, international competition in Shenzhen China, first place \hspace*{\fill} Jul 2018}
            
            % \textbf{Hack@NECST:} \textit{Heart rate (ECG) signal analysis using deep convolutional neural networks on FPGA, second place \hspace*{\fill} Jul 2017}

       \vspace{-13pt}
        
    \section{Projects}
    \vspace{-2pt}
        
        \textbf{Embedded firmware:} \textit{'Project Sparthan: Open source prosthetics development kit'
        \hspace*{\fill} Jan 2018 - Current}
        {
        \begin{itemize}
            \item Sparthan aims to provide children with responsive, low-cost, 3D printed prosthetic hands controlled by muscles' signals (EMG).
            \item Created schematics and board layout for custom printed circuit board (PCB) in Altium Designer to reduce the device's footprint.
            \item Developed a feed-forward neural network architecture in C++ running on STM32 micro-controller for hand gesture classification.
        \end{itemize}
        }
        \vspace{2pt}
        
        % \textbf{Embedded firmware:} \textit{'Beyond Hands: 3D printed, application specific prostheses'  
        % \hspace*{\fill} Sep 2018 - May 2019}
        % \small{\begin{itemize}
        %     \item Beyond Hands is an initiative of BEST lab at the University of California Berkeley, aimed at developing prosthetics for musicians.
        %     \item Designed the firmware for an electronic, PID controlled variable stiffness actuator for intuitively changing the drumming rhythm.
        % \end{itemize}}
        
        % \vspace{2pt}
        
        \textbf{Embedded machine learning:} \textit{'An automatic ML-based characterization of lung cancer from  PET and CT'  
        \hspace*{\fill} Aug 2018 - Oct 2018}
        \small{\begin{itemize}
            \item Development of an advanced medical imaging analysis pipeline in collaboration with NECST Lab and Humanitas hospital in Milan.
            \item Designed an embedded machine learning approach using hardware accelerated classification on FPGA platform.
            \item Presented results and our python based prototyping framework as a keynote speaker at the Xilinx Design Forum in San Jose (CA).
        \end{itemize}}

      \vspace{-13pt}

    \section{Skills}
    
        \vspace{-2pt}
        
        \textbf{Programming:} C, C++, Rust, Python, Javascript (React), Matlab, Arduino, TeX, Verilog, VHDL, git
        
        \vspace{-1pt}
        
        \textbf{Languages:} Italian (Native), English (Fluent: TOEFL 117/120), Chinese Mandarin (Basic proficiency, HSK I 192/200)
        
        \vspace{-16pt}
        
        \hide{data science; convolutional neural network; deep learning; python; pandas; keras; matlab; random forest; extra tree classifier; robotic manipulation; signal processing; microfluidic devices; MEMS; STM32; microcontroller; WiFi; BLE; HTML; Javascript; React}

\end{document}
